Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-27 manuscript.Rmd
Fix reference format

## Social Cohesion
Real-world collective action is known to bring about a sense of togetherness, also known as “collective effervescence” [@durkheim1995elementary]. This feeling of being a part of something larger than oneself leads individuals to act in ways that would not have on their own. Being overcome with this feeling is known to lead to violence [@collins2009violence; @spaaij2014sports]. While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion. Gilligan, Pasquale, and Samii (2013) found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion. Just as real-world social cohesion can be quantified, the same is true for online cohesion. Strategic communication on social media in the form of social cohesion of language can lead to real-world social change, and exposure to real-world violence could result in social cohesion in the virtual world. Increased social cohesion is thus potentially an indicator of increased social organization and mobilization on the ground.

>>>>

## Social Cohesion
Real-world collective action is known to bring about a sense of togetherness, also known as “collective effervescence” [@durkheim1995elementary]. This feeling of being a part of something larger than oneself leads individuals to act in ways that would not have on their own. Being overcome with this feeling is known to lead to violence [@collins2009violence; @spaaij2014sports]. While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion. @gilligan2014civil found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion. Just as real-world social cohesion can be quantified, the same is true for online cohesion. Strategic communication on social media in the form of social cohesion of language can lead to real-world social change, and exposure to real-world violence could result in social cohesion in the virtual world. Increased social cohesion is thus potentially an indicator of increased social organization and mobilization on the ground.

### 2020-05-27 manuscript.tex
Fix reference format

Real-world collective action is known to bring about a sense of togetherness, also known as \enquote{collective effervescence} (Durkheim, 1995). This feeling of being a part of something larger than oneself leads individuals to act in ways that would not have on their own. Being overcome with this feeling is known to lead to violence (Collins, 2009; Spaaij, 2014). While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion. Gilligan, Pasquale, and Samii (2013) found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion. Just as real-world social cohesion can be quantified, the same is true for online cohesion. Strategic communication on social media in the form of social cohesion of language can lead to real-world social change, and exposure to real-world violence could result in social cohesion in the virtual world. Increased social cohesion is thus potentially an indicator of increased social organization and mobilization on the ground.

@@

>>>>

Real-world collective action is known to bring about a sense of togetherness, also known as \enquote{collective effervescence} (Durkheim, 1995). This feeling of being a part of something larger than oneself leads individuals to act in ways that would not have on their own. Being overcome with this feeling is known to lead to violence (Collins, 2009; Spaaij, 2014). While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion. Gilligan, Pasquale, and Samii (2014) found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion. Just as real-world social cohesion can be quantified, the same is true for online cohesion. Strategic communication on social media in the form of social cohesion of language can lead to real-world social change, and exposure to real-world violence could result in social cohesion in the virtual world. Increased social cohesion is thus potentially an indicator of increased social organization and mobilization on the ground.

@@

\leavevmode\hypertarget{ref-gilligan2014civil}{}%
Gilligan, M. J., Pasquale, B. J., \& Samii, C. (2014). Civil war and social cohesion: Lab-in-the-field evidence from nepal. \emph{American Journal of Political Science}, \emph{58}(3), 604--619.
